Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-11-26 patchy-selection-paper.tex
.

% sm=0.1
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/18885-r1-501-sb0.01-sm-0.1-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/56325-r1-501-sb0.01-sm-0.1-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/28432-r1-501-sb0.01-sm-0.1-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.1$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.01
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/43099-r1-501-sb0.01-sm-0.01-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/69787-r1-501-sb0.01-sm-0.01-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/11821-r1-501-sb0.01-sm-0.01-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.01$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.001
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/59611-r1-501-sb0.01-sm-0.001-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/93713-r1-501-sb0.01-sm-0.001-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/29850-r1-501-sb0.01-sm-0.001-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.0001
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/15449-r1-501-sb0.01-sm-1e-04-N1600-pophistory-run}.pdf}
    \includegraphics{{example-sims/5582-r1-501-sb0.01-sm-1e-04-N400-pophistory-run}.pdf}
    \includegraphics{{example-sims/24639-r1-501-sb0.01-sm-1e-04-N25-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

>>>>

% sm=0.1
\begin{figure}
  \begin{center}
    \includegraphics{{example-mutation-sims/18885-r1-501-sb0.01-sm-0.1-N1200-pophistory-run}.pdf}
    \includegraphics{{example-mutation-sims/56325-r1-501-sb0.01-sm-0.1-N600-pophistory-run}.pdf}
    \includegraphics{{example-mutation-sims/28432-r1-501-sb0.01-sm-0.1-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.1$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.01
\begin{figure}
  \begin{center}
    \includegraphics{{example-mutation-sims/43099-r1-501-sb0.01-sm-0.01-N1200-pophistory-run}.pdf}
    \includegraphics{{example-mutation-sims/69787-r1-501-sb0.01-sm-0.01-N600-pophistory-run}.pdf}
    \includegraphics{{example-mutation-sims/11821-r1-501-sb0.01-sm-0.01-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.01$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.001
\begin{figure}
  \begin{center}
    \includegraphics{{example-mutation-sims/59611-r1-501-sb0.01-sm-0.001-N1200-pophistory-run}.pdf}
    \includegraphics{{example-mutation-sims/93713-r1-501-sb0.01-sm-0.001-N600-pophistory-run}.pdf}
    \includegraphics{{example-mutation-sims/29850-r1-501-sb0.01-sm-0.001-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.0001
\begin{figure}
  \begin{center}
    \includegraphics{{example-mutation-sims/15449-r1-501-sb0.01-sm-1e-04-N1600-pophistory-run}.pdf}
    \includegraphics{{example-mutation-sims/5582-r1-501-sb0.01-sm-1e-04-N400-pophistory-run}.pdf}
    \includegraphics{{example-mutation-sims/24639-r1-501-sb0.01-sm-1e-04-N25-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}
